Sketch of DP - Bayesian Inference

### 2018-07-17 main-sketch.tex
section 3 finished

\section{The Problem and Baseline approach}
We are interested in designing a mechanism for privately releasing
\emph{fully} the posterior distributions derived in section \ref{sec_background},
and not a sample from them.  It's worth noticing that the posterior
distributions are fully characterized by their parameters, and the
family (beta, Dirichlet) they belong to.  Hence, in case of the
Beta-Binomial model we are interested in releasing a private version
of the pair of parameters $(\alpha',\beta')=(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$, and
in the case of the Dirichlet-Multinomial model we are interested in a
private version of $\valpha'=(\valpha + \Delta \valpha)$. \citet{zhang2016differential} and \citet{xiao2012bayesian} have
already attacked this problem and their solution consisted in adding
independent Laplacian noise to the parameters of the posteriors. That
is, in the case of the Beta-Binomial system the value released would
be: $(\tilde\alpha,\tilde\beta)=(\alpha + \Delta \tilde\alpha,\beta + n - \Delta \tilde\alpha)$ where $\Delta \tilde\alpha\sim Lap(\Delta \alpha, \frac{2}{\epsilon})$, and
%with truncating method come from algorithm designed by \citet{zhang2016differential}
where $Lap(\mu,\nu)$
denotes a Laplacian random variable with mean $\mu$ and scale $\nu$.
This mechanism is $\epsilon$-differentially private, and the noise is
calibrated w.r.t to a sensitivity of 2 which is derived by using
$\ell_1$ norm over the pair of parameters. Indeed, considering two
adjacent\footnote{Given $\dataobs, \dataobs'\in\{0,1\}^{n}$ we say that $\dataobs$ and $\dataobs'$ are adjacent and we write, $\adj{\dataobs}{\dataobs'}$, iff
$\displaystyle \sum_{i}^{n}\iverson{x_i = x'_i }\leq 1$ } data observations
$\dataobs, \dataobs'$, that, from a unique prior, give rise to two posterior
distributions, characterized by the pairs
$(\alpha',\beta')$ and $(\alpha'',\beta'')$ then
$|\alpha'-\alpha''|+|\beta'-\beta''|\leq 2$.
This argument extends similarly to the Dirichelet-Multinomial system.

@@

\begin{equation*}
\underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S_\beta(\dataobs)})}
{\displaystyle\sum_{r\in\betaset} exp(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S_{\beta}(\dataobs)})}
\end{equation*}
this mechanism is based on the basic exponential mechanism \cite{talwar}, with $\betaset$ as range and $\hellinger(\cdot,\cdot)$ as scoring function.
The difference is that in this mechanism we don't calibrate the noise w.r.t to the global sensitivity of the scoring function but w.r.t to the smooth sensitivity $S_{\beta}(\dataobs)$
-- \citet{nissim2007smooth}-- of $\hellinger(\bysinfer(\dataobs), \cdot)$. The smooth sensitivity is computed as follows:
\[
   S_{\beta}(\dataobs)=\max_{\dataobs' \neq \dataobs, \dataobs' \in \{0,1\}^{n}}\bigg \{\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )\cdot e^{-\gamma\cdot d(\dataobs, \dataobs')}\bigg\}
 \]

 where $d$ is the Hamming distance between two datasets,  $\gamma = \gamma(\epsilon, \delta)$ is a function
 of $\epsilon$ and $\delta$ to be determined later, and where $\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )$
 denotes the local sensitivity at $\bysinfer(\dataobs')$, or equivalently at $\dataobs'$ --w.r.t $\ell_1$ norm--of the scoring function used in our mechanism, that is:
 \begin{equation*}
 \Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )=\max_{\dataobs'' \in \datauni^n:\adj{\dataobs'}{\dataobs''}, r\in \betaset}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs''), r)\rvert
\end{equation*}

\subsection{Analysis of the mechanism}
% In what follows, we will use a correspondence between the probability
%  $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ of every
%  $r\in\betaset$ and the probability 
%  $\underset{z \thicksim \hexpmech(x)}{Pr}[\hlg(\bysinfer(x),z) =
%  \hlg(\bysinfer(x),r)]$ for the utility score for $r$. In particular, for every
%  $r\in\betaset$ we have:
% $$
% \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]=
% \frac{1}{2}\Big (\underset{z \thicksim \hexpmech(x)}{Pr}[\hlg(\bysinfer(x),z) =
%  \hlg(\bysinfer(x),r)]\Big )
% $$
% To see this, it is enough to notice that: $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ is proportional too $\hlg(\bysinfer(x),r)$, i.e., $u(x,z)$. We can derive, if $u(r,x) = u(r',x)$ then $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r] = \underset{z \thicksim \hexpmech(x)}{Pr}[z = r']$. We assume the number of candidates $z \in \mathcal{R}$ that satisfy $u(z,x) = u(r,x)$ is $|r|$, we have  $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = |r| \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$. Because Hellinger distance  $\hlg(\bysinfer(x),z)$ is axial symmetry, where the $\bysinfer(x)$ is the symmetry axis. It can be infer that $|z| = 2$ for any candidates, apart from the true output, i.e., $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = 2 \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$. This parameter can be eliminate in both sides in proof.

% In our private Bayesian inference mechanism, we set the $\beta$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$.

\begin{theorem}
The mechanism $\hexpmech$ is $(\epsilon,\delta)-$differential privacy by setting $\gamma$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, deduced from the proof of privacy.
\end{theorem}

This mechanism also extends to Dirichlet distribution $\dirichlet(\valpha)$ by rewriting the Hellinger distance as:
\[
\hellinger(\dirichlet(\valpha_1), \dirichlet(\valpha_2)) = \sqrt{1 - \frac{\betaf(\frac{\valpha_1 + \valpha_2}{2})}{\betaf(\valpha_1) \betaf(\valpha_2)}},
\]
and replacing the $\betaset$ with set of Dirichlet distribution candidates of the same dimension under the same settings. Notice that $\betaset$ has $\binom{n + 1}{m - 1}$ elements when extends to Dirichlet distribution.

>>>>

\section{The Problem and Baseline approach}
We are interested in designing a mechanism for privately releasing
\emph{fully} the posterior distributions derived in section \ref{sec_background},
and not a sample from them.  It's worth noticing that the posterior
distributions are fully characterized by their parameters, and the
family (beta, Dirichlet) they belong to.  Hence, in case of the
Beta-Binomial model we are interested in releasing a private version
of the pair of parameters $(\alpha',\beta')=(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$, and
in the case of the Dirichlet-Multinomial model we are interested in a
private version of $\valpha'=(\valpha + \Delta \valpha)$. \citet{zhang2016differential} and \citet{xiao2012bayesian} have
already attacked this problem and their solution consisted in adding
independent Laplacian noise to the parameters of the posteriors. That
is, in the case of the Beta-Binomial system the value released would
be: $(\tilde\alpha,\tilde\beta)=(\alpha + \Delta \tilde\alpha,\beta + n - \Delta \tilde\alpha)$ where $\Delta \tilde\alpha\sim Lap(\Delta \alpha, \frac{2}{\epsilon})$, and
%with truncating method come from algorithm designed by \citet{zhang2016differential}
where $Lap(\mu,\nu)$
denotes a Laplacian random variable with mean $\mu$ and scale $\nu$.
This mechanism is $\epsilon$-differentially private, and the noise is
calibrated w.r.t to a sensitivity of 2 which is derived by using
$\ell_1$ norm over the pair of parameters. Indeed, considering two
adjacent\footnote{Given $\dataobs, \dataobs'$  we say that $\dataobs$ and $\dataobs'$ are adjacent and we write, $\adj{\dataobs}{\dataobs'}$, iff\\
$\displaystyle \sum_{i}^{n}\iverson{x_i = x'_i }\leq 1$. } data observations
$\dataobs, \dataobs'$, that, from a unique prior, give rise to two posterior
distributions, characterized by the pairs
$(\alpha',\beta')$ and $(\alpha'',\beta'')$ then
$|\alpha'-\alpha''|+|\beta'-\beta''|\leq 2$.
This argument extends similarly to the Dirichelet-Multinomial system.

@@

\begin{equation*}
\underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)})}
{\displaystyle\sum_{r\in\betaset} exp(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)})}
\end{equation*}
this mechanism is based on the basic exponential mechanism \cite{talwar}, with $\betaset$ as range and $\hellinger(\cdot,\cdot)$ as scoring function.
The difference is that in this mechanism we don't calibrate the noise w.r.t to the global sensitivity of the scoring function but w.r.t to the smooth sensitivity $S(\dataobs)$
-- \citet{nissim2007smooth}-- of $\hellinger(\bysinfer(\dataobs), \cdot)$. The smooth sensitivity is computed as follows:
\begin{equation}
  \label{eq:smooth}
   S(\dataobs)=\max_{\dataobs' \neq \dataobs, \dataobs' \in \{0,1\}^{n}}\bigg \{\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )\cdot e^{-\gamma\cdot d(\dataobs, \dataobs')}\bigg\}
\end{equation}
 where $d$ is the Hamming distance between two datasets,  $\gamma = \gamma(\epsilon, \delta)$ is a function
 of $\epsilon$ and $\delta$ to be determined later, and where $\Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )$
 denotes the local sensitivity at $\bysinfer(\dataobs')$, or equivalently at $\dataobs'$ --w.r.t $\ell_1$ norm--of the scoring function used in our mechanism, that is:
 \begin{equation*}
 \Delta_{l}\bigg (\hellinger(\bysinfer(\dataobs'),\cdot)\bigg )=\max_{\dataobs'' \in \datauni^n:\adj{\dataobs'}{\dataobs''}, r\in \betaset}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs''), r)\rvert
\end{equation*}

This mechanism also extends to the Dirichlet-Multinomial system $\dirichlet(\valpha)$ by rewriting the Hellinger distance as:
\[
  \hellinger(\dirichlet(\valpha_1), \dirichlet(\valpha_2)) = \sqrt{1 - \frac{\betaf(\frac{\valpha_1 + \valpha_2}{2})}{\betaf(\valpha_1) \betaf(\valpha_2)}},
\]
and by replacing the $\betaset$ with set of posterior Dirichlet distributions candidates. Also, the smooth sensitivity $S(x)$ in (\ref{eq:smooth}) will be
computed by letting $\dataobs'$ range over all the elements in $\datauni^{n}$ adjacent to $\dataobs$.
Notice that $\betaset$ has $\binom{n + 1}{m - 1}$ elements in this case. We will denote by
$\hexpmechd$ the mechanism for the Dirichlet-Multinomial system.
% In what follows, we will use a correspondence between the probability
%  $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ of every
%  $r\in\betaset$ and the probability 
%  $\underset{z \thicksim \hexpmech(x)}{Pr}[\hlg(\bysinfer(x),z) =
%  \hlg(\bysinfer(x),r)]$ for the utility score for $r$. In particular, for every
%  $r\in\betaset$ we have:
% $$
% \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]=
% \frac{1}{2}\Big (\underset{z \thicksim \hexpmech(x)}{Pr}[\hlg(\bysinfer(x),z) =
%  \hlg(\bysinfer(x),r)]\Big )
% $$
% To see this, it is enough to notice that: $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ is proportional too $\hlg(\bysinfer(x),r)$, i.e., $u(x,z)$. We can derive, if $u(r,x) = u(r',x)$ then $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r] = \underset{z \thicksim \hexpmech(x)}{Pr}[z = r']$. We assume the number of candidates $z \in \mathcal{R}$ that satisfy $u(z,x) = u(r,x)$ is $|r|$, we have  $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = |r| \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$. Because Hellinger distance  $\hlg(\bysinfer(x),z)$ is axial symmetry, where the $\bysinfer(x)$ is the symmetry axis. It can be infer that $|z| = 2$ for any candidates, apart from the true output, i.e., $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = 2 \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$. This parameter can be eliminate in both sides in proof.

% In our private Bayesian inference mechanism, we set the $\beta$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$. 
The following result guarantees that the mechanisms are indeed differentially private.

\begin{theorem}[Privacy] 
  For  $\gamma=\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, then both
  $\hexpmech$ and $\hexpmechd$ are $(\epsilon,\delta)$-differentially private.
\end{theorem}
